### 2015-05-08 fundamentals/intro.tex
Reviewer 2: The manuscript has the following title: Fundamental Concepts in the Cyclus Fuel Cycle Simulator Framework and Modeling Ecosystem. It is not clear to me what and Modeling Ecosystem refers to.. Adds phrase to explain modeling ecosystem on first mention.

The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem
incorporate modern insights from simulation science and software architecture
to solve these problems.  These modern methods simultaneously enable more
efficient, accurate, robust, and validated analysis.  This next-generation fuel
cycle simulator is the result of design choices made to:

>>>>

The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem, 
the suite of agents and other physics plugins compatible with it,
incorporate modern insights from simulation science and software architecture
to solve these problems.  These modern methods simultaneously enable more
efficient, accurate, robust, and validated analysis.  This next-generation fuel
cycle simulator is the result of design choices made to:
